A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-10 papers/publication/paper-pollard.tex
initial reorg of intro

\section{Introduction and Related Work}

@@

Beyond the systems described by Doekemeijer and Varbanescu, the problem has compounded with the addition of even more proprietary and open source projects such as \cite{Cheramangalath:2015:Falcon}, \cite{Perez:2015:Ringo}, distributed memory approaches such as \cite{Hong:2015:PGX}. domain-specific languages \cite{Hong:2012:GreenMarl}, distributed database querying, \cite{Rodriguez:2015:Gremlin}, as well as novel communication schemes \cite{Edmonds:2013:ActiveMessages}. At the outset, this plethora of choices makes the question, ``which system is the best for my problem?'' daunting.

@@

Graphalytics \cite{Capota:2015:Graphalytics} also attempts to remedy these problems. However, in order for Graphalytics to analyze a graph processing system---Graphalytics calls these platforms---a programmer must implement Java classes as wrappers to call the particular implementations, satisfy dependencies, and set environment variables. These all require some knowledge of the inner workings of each system in addition to familiarity with the Graphalytics API.

>>>>

\section{Introduction}

%% What's the problem (motivation)

%% How do we address it?

Our contributions can be summarized as follows.
\begin{itemize}
\item
\item
\item
\end{itemize}

\section{Related Work}

@@

Beyond the systems described by Doekemeijer and Varbanescu, the problem has compounded with the addition of even more proprietary and open source projects such as \cite{Cheramangalath:2015:Falcon,Perez:2015:Ringo}, distributed memory approaches such as \cite{Hong:2015:PGX}. domain-specific languages \cite{Hong:2012:GreenMarl}, distributed database querying, \cite{Rodriguez:2015:Gremlin}, as well as novel communication schemes \cite{Edmonds:2013:ActiveMessages}. At the outset, this plethora of choices makes the question, ``which system is the best for my problem?'' daunting.

@@

Graphalytics \cite{Capota:2015:Graphalytics} attempts to automate the setup and execution of packages in order to compare performance. However, in order for Graphalytics to analyze a graph processing system---Graphalytics calls these platforms---a programmer must implement Java classes as wrappers to call the particular implementations, satisfy dependencies, and set environment variables. These all require some knowledge of the inner workings of each system in addition to familiarity with the Graphalytics API.
